Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/revisited.tex
fixups

A natural question to ask is why we had to introduce the relative reputation proportion instead of simply using the mean to understand the results. For instance, the following would have been a natural conjecture:
\begin{conjecture}\label{conj:mean-trajectories}
\item Given a sufficiently large $T_0$, if one algorithm's mean reputation trajectory lies above another (for instance, Figure  \ref{prelim_means}), then the first algorithm prevails in the competition game.
\end{conjecture}

>>>>

A natural question to ask is why we had to introduce the relative reputation proportion instead of simply using the mean to understand the results. For instance, the following would have been a natural conjecture:
\begin{conjecture}\label{conj:mean-trajectories}
Given a sufficiently large $T_0$, if one algorithm's mean reputation trajectory lies above another (for instance, Figure  \ref{prelim_means}), then the first algorithm prevails in the competition game.
\end{conjecture}
